---
title: "Step 6: descriptive analysis by western and eastern Europe"
author: "Endre Borbáth and Swen Hutter"
output: html_document
---

# Loading packages

```{r setup, include=FALSE}

library(readxl)
library(tidyr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(haven)
library(forcats)
library(ggrepel)
library(cowplot)
library(kableExtra)
library(corrplot)
library(tidytext)
library(sparkline)
library(ggtext)

set.seed(1991)

rm(list = ls()) 

load("dataset_long.Rdata")

range01 <- function(x){(x-min(x, na.rm = TRUE))/(max(x, na.rm = TRUE)-min(x, na.rm = TRUE))}

dat <- d_lng %>% 
  filter(democratization!="IIIrd wave in EE") %>% 
  arrange(country, party_id, year)

colors <- thematic::okabe_ito(8)[-6]

```

# Appendix C (Western Europe)


## Figure 1: Distribution of party names over time by region (a)


```{r, echo = F, message = F, warning = F, fig.height = 3.45, fig.width = 5.5, fig.align = "center"}

## Organizational and ideological dimensions separated - one plot - see descriptive analysis

dat_plot1 <- dat %>% 
  mutate(region=case_when(country_name %in% c("Bulgaria", "Czech Republic", "Czechia", 
                                              "Estonia", "Croatia", "Hungary", 
                                              "Lithuania", "Latvia", "Poland", 
                                              "Romania", "Slovakia", 
                                              "Slovenia") ~ "Eastern EU",
                          country_name %in% c("Austria", "Belgium", "Switzerland", 
                                              "Germany", "Denmark", "Spain", 
                                              "Finland", "France", "United Kingdom", 
                                              "Greece", "Ireland", "Italy", 
                                              "Luxembourg", "Netherlands", 
                                              "Norway", "Portugal", 
                                              "Sweden") ~ "Western EU",
                          TRUE ~ as.character(NA))) %>% 
  filter(region=="Western EU") %>% 
  mutate(broad_types=case_when(grepl("Ideological", typology) ~ "Ideological names",
                               grepl("Nonideological", typology) ~ "Nonideological names")) %>% 
  select(year, broad_types) %>% 
  group_by(year) %>%
  mutate(total_parties=n()) %>%
  ungroup(.) %>% 
  group_by(year, broad_types) %>% 
  mutate(nr_parties=n()) %>%
  ungroup(.) %>%
  select(year, broad_types, total_parties, nr_parties) %>%
  distinct(.) %>% 
  mutate(share_parties=nr_parties*100/total_parties) %>% 
  select(-total_parties, -nr_parties)

full_grid <- expand.grid(year=unique(dat_plot1$year), 
                         broad_types=unique(dat_plot1$broad_types))

dat_plot1 <- left_join(full_grid, dat_plot1) %>% 
  mutate(share_parties=ifelse(is.na(share_parties), 0, share_parties)) %>% 
  mutate(dimension="Ideological dimension") %>% 
  mutate(broad_types=factor(broad_types, levels=c("Ideological names", "Nonideological names")))

timeline1 <- ggplot(dat_plot1, aes(x=year, y = share_parties, linetype=broad_types, color=broad_types)) + 
  geom_line(size=0.75) +
  facet_wrap(~dimension, ncol=1) +
  ylab("Proportion from all names") +
  scale_x_discrete(limits=(seq(1945, 2023, 10))) +
  scale_color_manual(values=c("#0072B2", "#D55E00", "#009E73", "#CC79A7",  "#56B4E9")) +
  scale_linetype_manual(values=c("solid", "dotdash", "solid", "twodash", "dashed")) +
  guides(color = guide_legend(ncol =2, byrow=TRUE),
         linetype = guide_legend(ncol=2, byrow=TRUE)) +
  theme_linedraw() + 
  expand_limits(y = 0) +
  theme(
    legend.title = element_blank(), 
    legend.position = "bottom",
    # legend.justification = "left",   # Left-justify the legend *inside* the overall plot area
    # legend.box.just = "left",    # Align the boxes/items to the left as well
    legend.margin = margin(),
    axis.title.x = element_blank(),
    legend.key.width = unit(1, "cm")
  )
        # plot.margin=margin(t = 5, r = 15, b = 5, l = 5, unit = "pt")) 

timeline1

dat_plot2 <- dat %>% 
  mutate(region=case_when(country_name %in% c("Bulgaria", "Czech Republic", "Czechia", 
                                              "Estonia", "Croatia", "Hungary", 
                                              "Lithuania", "Latvia", "Poland", 
                                              "Romania", "Slovakia", 
                                              "Slovenia") ~ "Eastern EU",
                          country_name %in% c("Austria", "Belgium", "Switzerland", 
                                              "Germany", "Denmark", "Spain", 
                                              "Finland", "France", "United Kingdom", 
                                              "Greece", "Ireland", "Italy", 
                                              "Luxembourg", "Netherlands", 
                                              "Norway", "Portugal", 
                                              "Sweden") ~ "Western EU",
                          TRUE ~ as.character(NA))) %>% 
  filter(region=="Western EU") %>% 
  mutate(broad_types=case_when(grepl(" party", typology) ~ "Party names",
                               grepl("nonparty", typology) ~ "Nonparty names",
                               grepl("movement", typology) ~ "Movement names")) %>% 
  select(year, broad_types) %>% 
  group_by(year) %>%
  mutate(total_parties=n()) %>%
  ungroup(.) %>% 
  group_by(year, broad_types) %>% 
  mutate(nr_parties=n()) %>%
  ungroup(.) %>%
  select(year, broad_types, total_parties, nr_parties) %>%
  distinct(.) %>% 
  mutate(share_parties=nr_parties*100/total_parties) %>% 
  select(-total_parties, -nr_parties)

full_grid <- expand.grid(year=unique(dat_plot2$year), 
                         broad_types=unique(dat_plot2$broad_types))

dat_plot2 <- left_join(full_grid, dat_plot2) %>% 
  mutate(share_parties=ifelse(is.na(share_parties), 0, share_parties)) %>% 
  mutate(dimension="Organizational dimension") %>% 
  mutate(broad_types=factor(broad_types, levels=c("Party names", "Nonparty names", "Movement names")))

timeline2 <- ggplot(dat_plot2, aes(x=year, y = share_parties, linetype=broad_types, color=broad_types)) + 
  geom_line(size=0.75) +
  facet_wrap(~dimension, ncol=1) +
  ylab("Proportion from all names") +
  scale_x_discrete(limits=(seq(1945, 2023, 10))) +
  scale_color_manual(values=c("#009E73", "#CC79A7",  "#56B4E9")) +
  scale_linetype_manual(values=c("solid", "twodash", "dashed")) +
  guides(color = guide_legend(ncol =3, byrow=TRUE),
         linetype = guide_legend(ncol=3, byrow=TRUE)) +
  theme_linedraw() + 
  expand_limits(y = 0) +
  theme(
    legend.title = element_blank(), 
    legend.position = "bottom",
    # legend.justification = "left",   # Left-justify the legend *inside* the overall plot area
    # legend.box.just = "left",    # Align the boxes/items to the left as well
    legend.margin = margin(),
    axis.title.x = element_blank(),
    legend.key.width = unit(1, "cm")
  )
        # plot.margin=margin(t = 5, r = 15, b = 5, l = 5, unit = "pt")) 

timeline2

cowplot::plot_grid(timeline1, timeline2, ncol=1)

ggsave(plot=last_plot(),
      filename = "Figure3_west.png",
      path="appendix/figures/", scale = 2,
      width = 6, height = 7, dpi=400, units="cm")
  

```

## Figure 2: Distribution of party names by region (a)

```{r, echo = F, message = F, warning = F, fig.height = 3.45, fig.width = 5.5, fig.align = "center"}

library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

# Create the graph
decision_tree <- grViz("
digraph decision_tree {

  # Node definitions with labels
  node [shape = box, style = filled, color = white]
  A [label = <Ideological<br/>name>]
  B [label = <Nonideological<br/>name>]
A1 [label = <<b>Classical<br/>party name</b><br/>25% (112)>]
A2 [label = <Nonparty<br/>name<br/>26% (114)>]
A3 [label = <Movement<br/>name<br/>6% (25)>]
B1 [label = <Party<br/>name<br/>10% (46)>]
B2 [label = <<b>Nonparty<br/>name</b><br/>27% (121)>]
B3 [label = <<b>Movement<br/>name</b><br/>6% (25)>]

  # Connections between nodes
  node [shape = box, style = filled, color = white]
  root [label = 'The name of the party']

  root -> A
  root -> B
  A -> A1
  A -> A2
  A -> A3
  B -> B1
  B -> B2
  B -> B3
}
")

# Export the graph to a PNG file

svg_code <- export_svg(decision_tree)

rsvg_png(charToRaw(svg_code), file = "appendix/figures/decision_tree_west.png", width = 7200, height = 3320)

writeLines(svg_code, "appendix/figures/decision_tree_west.svg")

## for a table - see the file descriptive analysis

```


```{r, echo = F, message = F, warning = F, fig.height = 3.45, fig.width = 5.5, fig.align = "center"}

dat_plot1 <- dat %>% 
  select(party_id, typology) %>% 
  group_by(party_id, typology) %>%
  unique() %>% 
  ungroup(.) %>% 
  mutate(total_parties=n()) %>%
  group_by(typology) %>% 
  mutate(nr_parties=n()) %>%
  ungroup(.) %>%
  select(typology, total_parties, nr_parties) %>% 
  distinct(.) 

dat_plot2 <- dat_plot1

dat_plot1 <- dat_plot1 %>% 
  mutate(share_parties=nr_parties*100/total_parties) %>% 
  mutate(share_abs_number=paste0(round(share_parties, 0), "% (", nr_parties, ")")) %>%
  select(-total_parties, -nr_parties, -share_parties) %>%
  distinct(.) %>% 
  rename(Type=typology) %>%
  select(Type, share_abs_number) %>% 
  arrange(Type)

dat_plot2 <- dat_plot2 %>% 
  mutate(nr_parties=sum(nr_parties, na.rm=TRUE)) %>%
  select(-typology) %>% 
  distinct() %>% 
  mutate(share_parties=nr_parties*100/total_parties) %>% 
  mutate(share_abs_number=paste0(round(share_parties, 0), "% (", nr_parties, ")")) %>%
  select(-total_parties, -nr_parties, -share_parties) %>%
  mutate(Type="Overall") %>% 
  select(Type, share_abs_number) 

dat_plot1 <- bind_rows(dat_plot1, dat_plot2) %>% 
  mutate(across(everything(), ~ ifelse(is.na(.), "", .)))

table_latex <-  kbl(dat_plot1,
      caption = "Distribution of party brand types (1945-2023) \\label{tab:average_distributions}",
      booktabs = T, format = "latex", linesep = "",
      col.names = c("Type", "Share (count)")) %>% 
  kable_styling(latex_options = "HOLD_position") %>%   # Change will be here
  # Bold the header row, and ensure a \hline after it as well
  row_spec(0, bold = TRUE) %>%
  column_spec(1, bold = ifelse(dat_plot1$Type == "Overall", TRUE, FALSE)) %>%
  # Also ensure we get a line after the last row (row 7).
  row_spec(nrow(dat_plot1)-1, hline_after = TRUE) %>%
  footnote(general = "Note: Relative shares are calculated from the total number of unique party names. In paranthesis the number of unique party names in the respective category.", general_title="", threeparttable = TRUE)

cat(table_latex)
  
# writeLines(table_latex, paste0(path, "Appendix/", month, "/Tables/distribution_types.tex"))
  
```

## Figure 3: Distribution of party names by party family (a)

```{r, echo = F, message = F, warning = F, fig.height = 3.45, fig.width = 5.5, fig.align = "center"}

dat_plot1 <- dat %>% 
  mutate(indic=ifelse(typology=="Ideological party", 1, 0)) %>% 
  group_by(party_id, family_name) %>% 
  mutate(nr_parties=sum(indic, na.rm=TRUE)) %>% 
  select(family_name, nr_parties, party_id) %>% 
  unique(.) %>% 
  ungroup(.) %>% 
  mutate(indic=ifelse(nr_parties>0, 1, 0)) %>% 
  group_by(family_name) %>% 
  mutate(total=n()) %>% 
  mutate(indic=sum(indic)) %>%
  select(-party_id, -nr_parties) %>% 
  unique(.) %>% 
  mutate(share=indic/total*100) %>% 
  mutate(no_party="Ideological party") %>% 
  rename(DV=no_party) %>%
  ungroup(.) %>% 
  arrange(share) %>% 
  mutate(ranking=row_number())

dat_plot2 <- dat %>% 
  mutate(indic=ifelse(typology=="Nonideological nonparty", 1, 0)) %>%  
  group_by(party_id, family_name) %>% 
  mutate(nr_parties=sum(indic, na.rm=TRUE)) %>% 
  select(family_name, nr_parties, party_id) %>% 
  unique(.) %>% 
  ungroup(.) %>% 
  mutate(indic=ifelse(nr_parties>0, 1, 0)) %>% 
  group_by(family_name) %>% 
  mutate(total=n()) %>% 
  mutate(indic=sum(indic)) %>%
  select(-party_id, -nr_parties) %>% 
  unique(.) %>% 
  mutate(share=indic/total*100) %>% 
  mutate(action_based="Nonideological nonparty") %>% 
  rename(DV=action_based)

dat_plot3 <- dat %>% 
  mutate(indic=ifelse(typology=="Nonideological movement", 1, 0)) %>% 
  group_by(party_id, family_name) %>% 
  mutate(nr_parties=sum(indic, na.rm=TRUE)) %>% 
  select(family_name, nr_parties, party_id) %>% 
  unique(.) %>% 
  ungroup(.) %>% 
  mutate(indic=ifelse(nr_parties>0, 1, 0)) %>% 
  group_by(family_name) %>% 
  mutate(total=n()) %>% 
  mutate(indic=sum(indic)) %>%
  select(-party_id, -nr_parties) %>% 
  unique(.) %>%  
  mutate(share=indic/total*100) %>% 
  mutate(catch_all_ref="Nonideological movement") %>% 
  rename(DV=catch_all_ref)

dat_plot <- bind_rows(dat_plot1, dat_plot2, dat_plot3) %>% 
  select(-ranking) %>% 
  ungroup(.) %>% 
  filter(!(family_name %in% c("to be coded", "Special issue", "no family"))) %>% 
  mutate(DV=case_when(DV=="Ideological party" ~ "Classical party\nname",
                      DV=="Nonideological nonparty" ~ "Nonideological\nnonparty name",
                      DV=="Nonideological movement" ~ "Nonideological\nmovement name")) %>%
  mutate(DV=factor(DV, levels=c("Classical party\nname", "Nonideological\nnonparty name", 
                                "Nonideological\nmovement name"))) %>% 
  # mutate(DV=fct_rev(DV)) %>% 
  mutate(family_name=factor(family_name, levels=c("Communist/Socialist", "Social democracy",
                                                  "Green/Ecologist", "Christian democracy", "Liberal", 
                                                  "Conservative", "Agrarian", "Right-wing"))) %>% 
  mutate(family_name=fct_rev(family_name))
  
rm(dat_plot1, dat_plot2, dat_plot3, totals)

# dat_plot$family_name <- factor(dat_plot$family_name, levels = unique(dat_plot$family_name[order(dat_plot$ranking, decreasing = FALSE)]))

rm(dat_plot1, dat_plot2, dat_plot3, totals)


ggplot(dat_plot, aes(y = family_name, x=share)) + #, fill=color_indic
  geom_col(color="black", show.legend = FALSE) + 
  facet_wrap(~DV, scales = "free_x", ncol=3) +
  scale_y_reordered() +
  xlab("Proportion of parties (pp. within party family)") +
  theme_linedraw() +
  # scale_fill_manual(name="", values=c("gray80", "gray40")) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE, reverse = TRUE)) +
  theme(legend.title=element_blank(), 
        legend.position="none",
        axis.title.y=element_blank())

ggsave(plot=last_plot(),
      filename = "Figure4_west.png",
      path="appendix/figures/", scale = 3,
      width = 6, height = 2.5, dpi=400, units="cm")

```

## Table 1: Distribution of brands in Western Europe


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}
dat <- dat %>% 
  mutate(dep_vars=case_when(typology=="Ideological party" ~ 1,
                            TRUE ~ 0))

groupped_share <- function(data, group_var) {

group_var <- enquo(group_var)

dat_plot <- dat %>% 
  mutate(past_pm = case_when(past_pm == "has been/is pm party" ~ 1,
                             past_pm == "no pm party" ~ 0),
         mainstream_family = case_when(family_name_short %in% c("chr", "con", "lib", "soc") ~ 1,
                                       TRUE ~ as.numeric(0)),
         opp_party = case_when(cabinet_party == 0 ~ 1,
                               cabinet_party == 1 ~ 0),
         econ_left = case_when(state_market>5 ~ 0,
                               state_market<=5 ~ 1),
         cult_progressive=case_when(liberty_authority>5 ~ 0,
                               liberty_authority<=5 ~ 1)) %>% 
  select(country, party_id, !!group_var, dep_vars) %>%
  group_by(country, !!group_var, dep_vars) %>% 
  mutate(by_var=n_distinct(party_id)) %>% 
  select(-party_id) %>% 
  unique(.) %>% 
  group_by(country, !!group_var) %>% 
  mutate(total=sum(by_var)) %>%
  ungroup(.) %>% 
  mutate(share=by_var/total) %>% 
  select(country, share, dep_vars, !!group_var, total) %>% 
  mutate(group_val=!!group_var) %>% 
  mutate(group_var=as_label(group_var)) %>% 
  unique(.) %>% 
  arrange(country, dep_vars) %>% 
  select(-!!group_var)

return(dat_plot)

}

dat_plot <- groupped_share(dat_plot, mainstream_family) 
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, past_pm))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, opp_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, new_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, econ_left))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, cult_progressive))

dat_plot <- dat_plot %>%
  arrange(country, group_var, dep_vars) %>%
  filter(!is.na(group_val)) %>%
  filter(dep_vars==1) %>% 
  select(-dep_vars)
  

full_list <- expand.grid(country=unique(dat_plot$country),
                         group_var=unique(dat_plot$group_var),
                         group_val=unique(dat_plot$group_val))

dat_plot <- left_join(full_list, dat_plot) %>% 
  mutate_at(vars(share, total), ~ifelse(is.na(.), 0, .)) %>% 
  group_by(group_var, group_val) %>% 
  mutate(share=mean(share)) %>% 
  mutate(total=sum(total)) %>% 
  select(-country) %>% 
  distinct(.) %>% 
  pivot_wider(id_cols = "group_var", names_from = "group_val", values_from = c("share", "total"))


for (i in seq(1, nrow(dat_plot), 1)) {

xsample <- sample(c(rep(1, round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0)), 
             rep(0, dat_plot$total_0[i]-round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0))))

ysample <- sample(c(rep(1, round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0)), 
             rep(0, dat_plot$total_1[i]-round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0))))

test <- t.test(xsample, ysample, alternative = "two.sided")

dat_plot$p_value[i] <- test$p.value

}

dat_plot <- dat_plot %>% 
  select(-contains("total")) %>% 
  mutate(p_value = case_when(p_value<0.05 ~ 1, 
                             TRUE ~ 0)) %>% 
  mutate(diff=share_0-share_1) 

ideological_party <- dat_plot  %>% 
  pivot_longer(cols=c(share_1, share_0), names_to = "dummy", values_to = "share") %>% 
  mutate(type = "Ideological party")

```


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}

dat <- dat %>% 
  mutate(dep_vars=case_when(typology=="Nonideological nonparty" ~ 1,
                            TRUE ~ 0))

dat_plot <- groupped_share(dat_plot, mainstream_family) 
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, past_pm))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, opp_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, new_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, econ_left))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, cult_progressive))

dat_plot <- dat_plot %>%
  arrange(country, group_var, dep_vars) %>%
  filter(!is.na(group_val)) %>%
  filter(dep_vars==1) %>% 
  select(-dep_vars)
  

full_list <- expand.grid(country=unique(dat_plot$country),
                         group_var=unique(dat_plot$group_var),
                         group_val=unique(dat_plot$group_val))

dat_plot <- left_join(full_list, dat_plot) %>% 
  mutate_at(vars(share, total), ~ifelse(is.na(.), 0, .)) %>% 
  group_by(group_var, group_val) %>% 
  mutate(share=mean(share)) %>% 
  mutate(total=sum(total)) %>% 
  select(-country) %>% 
  distinct(.) %>% 
  pivot_wider(id_cols = "group_var", names_from = "group_val", values_from = c("share", "total"))


for (i in seq(1, nrow(dat_plot), 1)) {

xsample <- sample(c(rep(1, round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0)), 
             rep(0, dat_plot$total_0[i]-round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0))))

ysample <- sample(c(rep(1, round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0)), 
             rep(0, dat_plot$total_1[i]-round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0))))

test <- t.test(xsample, ysample, alternative = "two.sided")

dat_plot$p_value[i] <- test$p.value

}

dat_plot <- dat_plot %>% 
  select(-contains("total")) %>% 
  mutate(p_value = case_when(p_value<0.05 ~ 1, 
                             TRUE ~ 0)) %>% 
  mutate(diff=share_0-share_1) 

nonideological_nonparty <- dat_plot %>% 
  pivot_longer(cols=c(share_1, share_0), names_to = "dummy", values_to = "share") %>% 
  mutate(type = "Nonideological nonparty")

```


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}

dat <- dat %>% 
  mutate(dep_vars=case_when(typology=="Nonideological movement" ~ 1,
                            TRUE ~ 0))

dat_plot <- groupped_share(dat_plot, mainstream_family) 
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, past_pm))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, opp_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, new_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, econ_left))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, cult_progressive))

dat_plot <- dat_plot %>%
  arrange(country, group_var, dep_vars) %>%
  filter(!is.na(group_val)) %>%
  filter(dep_vars==1) %>% 
  select(-dep_vars)
  

full_list <- expand.grid(country=unique(dat_plot$country),
                         group_var=unique(dat_plot$group_var),
                         group_val=unique(dat_plot$group_val))

dat_plot <- left_join(full_list, dat_plot) %>% 
  mutate_at(vars(share, total), ~ifelse(is.na(.), 0, .)) %>% 
  group_by(group_var, group_val) %>% 
  mutate(share=mean(share)) %>% 
  mutate(total=sum(total)) %>% 
  select(-country) %>% 
  distinct(.) %>% 
  pivot_wider(id_cols = "group_var", names_from = "group_val", values_from = c("share", "total"))


for (i in seq(1, nrow(dat_plot), 1)) {

xsample <- sample(c(rep(1, round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0)), 
             rep(0, dat_plot$total_0[i]-round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0))))

ysample <- sample(c(rep(1, round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0)), 
             rep(0, dat_plot$total_1[i]-round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0))))

test <- t.test(xsample, ysample, alternative = "two.sided")

dat_plot$p_value[i] <- test$p.value

}

dat_plot <- dat_plot %>% 
  select(-contains("total")) %>% 
  mutate(p_value = case_when(p_value<0.05 ~ 1, 
                             TRUE ~ 0)) %>% 
  mutate(diff=share_0-share_1) 

nonideological_movement <- dat_plot %>% 
  pivot_longer(cols=c(share_1, share_0), names_to = "dummy", values_to = "share") %>% 
  mutate(type = "Nonideological movement")

```


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}

dat_plot <- bind_rows(ideological_party, nonideological_nonparty, nonideological_movement) %>% 
  filter(!(group_var %in% c("cult_progressive", "econ_left", "opp_party"))) %>% 
    mutate(group_var=case_when(group_var=="mainstream_family" & dummy=="share_1" ~ "Mainstream party family",
                               group_var=="mainstream_family" & dummy=="share_0" ~ "Challenger party family",
                        group_var=="past_pm" & dummy=="share_1" ~ "Previously PM party",
                        group_var=="past_pm" & dummy=="share_0" ~ "Previously no PM party",
                        group_var=="opp_party" & dummy=="share_1" ~ "Opposition party",
                        group_var=="opp_party" & dummy=="share_0" ~ "Government party",
                        group_var=="new_party" & dummy=="share_1" ~ "New party",
                        group_var=="new_party" & dummy=="share_0" ~ "Existing party")) %>%
  mutate(diff=ifelse(dummy=="share_0", NA, diff)) %>% 
  select(-dummy) %>% 
  pivot_wider(id_cols = c(group_var), values_from = c(p_value, share, diff), names_from = type) %>% 
  mutate(group_var=factor(group_var, levels = c("Mainstream party family",
                                                "Challenger party family",
                                                "Previously PM party", 
                                                "Previously no PM party",
                                                "Opposition party",
                                                "Government party",
                                                "New party",
                                                "Existing party"))) %>% 
  arrange(group_var)


ideological_party_pval <- dat_plot$`p_value_Ideological party`
nonideological_nonparty_pval <- dat_plot$`p_value_Nonideological nonparty`
nonideological_movement_pval <- dat_plot$`p_value_Nonideological movement`

dat_plot <- dat_plot %>% 
  select(!contains("p_value")) %>% 
  select("group_var", "share_Ideological party", "diff_Ideological party", "share_Nonideological nonparty", "diff_Nonideological nonparty", "share_Nonideological movement", "diff_Nonideological movement") %>% 
  mutate_at(vars(contains(c("share_", "diff_"))), ~round(.*100, digits = 1)) %>% 
  mutate_at(vars(contains(c("diff_"))), ~0-.) 

options(knitr.kable.NA = "")

mod_res <- dat_plot %>%
  kbl(caption = "Distribution of brands in Western Europe \\label{tab:ttest_table}",
      booktabs = T, format = "latex", col.names = NULL, linesep = "") %>% 
  # kable_styling(latex_options = c("hold_position")) %>% 
  kable_styling(latex_options = "HOLD_position") %>%   # Change will be here
  column_spec(3, bold = ideological_party_pval) %>%
  column_spec(5, bold = nonideological_nonparty_pval) %>%
  column_spec(7, bold = nonideological_movement_pval) %>%
  add_header_above(c(" " = 1, "Share" = 1, "Diff." = 1, "Share" = 1, "Diff." = 1, "Share" = 1, "Diff." = 1)) %>%
  add_header_above(c(" " = 1, "Classical \n party \n name" = 2, 
                        "Nonideological \n nonparty \n name" = 2, 
                        "Nonideological \n movement \n name" = 2)) %>% 
  footnote(general = "Note: The values are averaged across all countries.", general_title="")
  
writeLines(mod_res, "appendix/tables/Table1_west.tex")

```


# Appendix C (Eastern Europe)


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}

dat <- d_lng %>% 
  filter(democratization=="IIIrd wave in EE") %>% 
  arrange(country, party_id, year)

```


## Figure 1: Distribution of party names over time by region (b)

```{r, echo = F, message = F, warning = F, fig.height = 3.45, fig.width = 5.5, fig.align = "center"}

## Organizational and ideological dimensions separated - one plot - see descriptive analysis

dat_plot1 <- dat %>% 
  mutate(region=case_when(country_name %in% c("Bulgaria", "Czech Republic", "Czechia", 
                                              "Estonia", "Croatia", "Hungary", 
                                              "Lithuania", "Latvia", "Poland", 
                                              "Romania", "Slovakia", 
                                              "Slovenia") ~ "Eastern EU",
                          country_name %in% c("Austria", "Belgium", "Switzerland", 
                                              "Germany", "Denmark", "Spain", 
                                              "Finland", "France", "United Kingdom", 
                                              "Greece", "Ireland", "Italy", 
                                              "Luxembourg", "Netherlands", 
                                              "Norway", "Portugal", 
                                              "Sweden") ~ "Western EU",
                          TRUE ~ as.character(NA))) %>% 
  filter(region=="Eastern EU") %>% 
  mutate(broad_types=case_when(grepl("Ideological", typology) ~ "Ideological names",
                               grepl("Nonideological", typology) ~ "Nonideological names")) %>% 
  select(year, broad_types) %>% 
  group_by(year) %>%
  mutate(total_parties=n()) %>%
  ungroup(.) %>% 
  group_by(year, broad_types) %>% 
  mutate(nr_parties=n()) %>%
  ungroup(.) %>%
  select(year, broad_types, total_parties, nr_parties) %>%
  distinct(.) %>% 
  mutate(share_parties=nr_parties*100/total_parties) %>% 
  select(-total_parties, -nr_parties)

full_grid <- expand.grid(year=unique(dat_plot1$year), 
                         broad_types=unique(dat_plot1$broad_types))

dat_plot1 <- left_join(full_grid, dat_plot1) %>% 
  mutate(share_parties=ifelse(is.na(share_parties), 0, share_parties)) %>% 
  mutate(dimension="Ideological dimension") %>% 
  mutate(broad_types=factor(broad_types, levels=c("Ideological names", "Nonideological names")))

timeline1 <- ggplot(dat_plot1, aes(x=year, y = share_parties, linetype=broad_types, color=broad_types)) + 
  geom_line(size=0.75) +
  facet_wrap(~dimension, ncol=1) +
  ylab("Proportion from all names") +
  scale_x_discrete(limits=(seq(1989, 2023, 3))) +
  scale_color_manual(values=c("#0072B2", "#D55E00", "#009E73", "#CC79A7",  "#56B4E9")) +
  scale_linetype_manual(values=c("solid", "dotdash", "solid", "twodash", "dashed")) +
  guides(color = guide_legend(ncol =2, byrow=TRUE),
         linetype = guide_legend(ncol=2, byrow=TRUE)) +
  theme_linedraw() + 
  expand_limits(y = 0) +
  theme(
    legend.title = element_blank(), 
    legend.position = "bottom",
    # legend.justification = "left",   # Left-justify the legend *inside* the overall plot area
    # legend.box.just = "left",    # Align the boxes/items to the left as well
    legend.margin = margin(),
    axis.title.x = element_blank(),
    legend.key.width = unit(1, "cm")
  )
        # plot.margin=margin(t = 5, r = 15, b = 5, l = 5, unit = "pt")) 

timeline1

dat_plot2 <- dat %>% 
  mutate(region=case_when(country_name %in% c("Bulgaria", "Czech Republic", "Czechia", 
                                              "Estonia", "Croatia", "Hungary", 
                                              "Lithuania", "Latvia", "Poland", 
                                              "Romania", "Slovakia", 
                                              "Slovenia") ~ "Eastern EU",
                          country_name %in% c("Austria", "Belgium", "Switzerland", 
                                              "Germany", "Denmark", "Spain", 
                                              "Finland", "France", "United Kingdom", 
                                              "Greece", "Ireland", "Italy", 
                                              "Luxembourg", "Netherlands", 
                                              "Norway", "Portugal", 
                                              "Sweden") ~ "Western EU",
                          TRUE ~ as.character(NA))) %>% 
  filter(region=="Eastern EU") %>% 
  mutate(broad_types=case_when(grepl(" party", typology) ~ "Party names",
                               grepl("nonparty", typology) ~ "Nonparty names",
                               grepl("movement", typology) ~ "Movement names")) %>% 
  select(year, broad_types) %>% 
  group_by(year) %>%
  mutate(total_parties=n()) %>%
  ungroup(.) %>% 
  group_by(year, broad_types) %>% 
  mutate(nr_parties=n()) %>%
  ungroup(.) %>%
  select(year, broad_types, total_parties, nr_parties) %>%
  distinct(.) %>% 
  mutate(share_parties=nr_parties*100/total_parties) %>% 
  select(-total_parties, -nr_parties)

full_grid <- expand.grid(year=unique(dat_plot2$year), 
                         broad_types=unique(dat_plot2$broad_types))

dat_plot2 <- left_join(full_grid, dat_plot2) %>% 
  mutate(share_parties=ifelse(is.na(share_parties), 0, share_parties)) %>% 
  mutate(dimension="Organizational dimension") %>% 
  mutate(broad_types=factor(broad_types, levels=c("Party names", "Nonparty names", "Movement names")))

timeline2 <- ggplot(dat_plot2, aes(x=year, y = share_parties, linetype=broad_types, color=broad_types)) + 
  geom_line(size=0.75) +
  facet_wrap(~dimension, ncol=1) +
  ylab("Proportion from all names") +
  scale_x_discrete(limits=(seq(1989, 2023, 3))) +
  scale_color_manual(values=c("#009E73", "#CC79A7",  "#56B4E9")) +
  scale_linetype_manual(values=c("solid", "twodash", "dashed")) +
  guides(color = guide_legend(ncol =3, byrow=TRUE),
         linetype = guide_legend(ncol=3, byrow=TRUE)) +
  theme_linedraw() + 
  expand_limits(y = 0) +
  theme(
    legend.title = element_blank(), 
    legend.position = "bottom",
    # legend.justification = "left",   # Left-justify the legend *inside* the overall plot area
    # legend.box.just = "left",    # Align the boxes/items to the left as well
    legend.margin = margin(),
    axis.title.x = element_blank(),
    legend.key.width = unit(1, "cm")
  )
        # plot.margin=margin(t = 5, r = 15, b = 5, l = 5, unit = "pt")) 

timeline2

cowplot::plot_grid(timeline1, timeline2, ncol=1)

ggsave(plot=last_plot(),
      filename = "Figure3_east.png",
      path= "appendix/figures/", scale = 2,
      width = 6, height = 7, dpi=400, units="cm")
  

```

## Figure 2: Distribution of party names by region (b)

```{r, echo = F, message = F, warning = F, fig.height = 3.45, fig.width = 5.5, fig.align = "center"}

library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

# Create the graph
decision_tree <- grViz("
digraph decision_tree {

  # Node definitions with labels
  node [shape = box, style = filled, color = white]
  A [label = <Ideological<br/>name>]
  B [label = <Nonideological<br/>name>]
A1 [label = <<b>Classical<br/>party name</b><br/>18% (66)>]
A2 [label = <Nonparty<br/>name<br/>20% (70)>]
A3 [label = <Movement<br/>name<br/>3% (11)>]
B1 [label = <Party<br/>name<br/>18% (63)>]
B2 [label = <<b>Nonparty<br/>name</b><br/>33% (119)>]
B3 [label = <<b>Movement<br/>name</b><br/>8% (29)>]

  # Connections between nodes
  node [shape = box, style = filled, color = white]
  root [label = 'The name of the party']

  root -> A
  root -> B
  A -> A1
  A -> A2
  A -> A3
  B -> B1
  B -> B2
  B -> B3
}
")

# Export the graph to a PNG file

svg_code <- export_svg(decision_tree)

rsvg_png(charToRaw(svg_code), file = "appendix/figures/decision_tree_east.png", width = 7200, height = 3320)

writeLines(svg_code, "appendix/figures/decision_tree_east.svg")

## for a table - see the file descriptive analysis

```


```{r, echo = F, message = F, warning = F, fig.height = 3.45, fig.width = 5.5, fig.align = "center"}

dat_plot1 <- dat %>% 
  select(party_id, typology) %>% 
  group_by(party_id, typology) %>%
  unique() %>% 
  ungroup(.) %>% 
  mutate(total_parties=n()) %>%
  group_by(typology) %>% 
  mutate(nr_parties=n()) %>%
  ungroup(.) %>%
  select(typology, total_parties, nr_parties) %>% 
  distinct(.) 

dat_plot2 <- dat_plot1

dat_plot1 <- dat_plot1 %>% 
  mutate(share_parties=nr_parties*100/total_parties) %>% 
  mutate(share_abs_number=paste0(round(share_parties, 0), "% (", nr_parties, ")")) %>%
  select(-total_parties, -nr_parties, -share_parties) %>%
  distinct(.) %>% 
  rename(Type=typology) %>%
  select(Type, share_abs_number) %>% 
  arrange(Type)

dat_plot2 <- dat_plot2 %>% 
  mutate(nr_parties=sum(nr_parties, na.rm=TRUE)) %>%
  select(-typology) %>% 
  distinct() %>% 
  mutate(share_parties=nr_parties*100/total_parties) %>% 
  mutate(share_abs_number=paste0(round(share_parties, 0), "% (", nr_parties, ")")) %>%
  select(-total_parties, -nr_parties, -share_parties) %>%
  mutate(Type="Overall") %>% 
  select(Type, share_abs_number) 

dat_plot1 <- bind_rows(dat_plot1, dat_plot2) %>% 
  mutate(across(everything(), ~ ifelse(is.na(.), "", .)))

table_latex <-  kbl(dat_plot1,
      caption = "Distribution of party brand types (1945-2023) \\label{tab:average_distributions}",
      booktabs = T, format = "latex", linesep = "",
      col.names = c("Type", "Share (count)")) %>% 
  kable_styling(latex_options = "HOLD_position") %>%   # Change will be here
  # Bold the header row, and ensure a \hline after it as well
  row_spec(0, bold = TRUE) %>%
  column_spec(1, bold = ifelse(dat_plot1$Type == "Overall", TRUE, FALSE)) %>%
  # Also ensure we get a line after the last row (row 7).
  row_spec(nrow(dat_plot1)-1, hline_after = TRUE) %>%
  footnote(general = "Note: Relative shares are calculated from the total number of unique party names. In paranthesis the number of unique party names in the respective category.", general_title="", threeparttable = TRUE)

cat(table_latex)
  
```

## Figure 3: Distribution of party names by party family (b)

```{r, echo = F, message = F, warning = F, fig.height = 3.45, fig.width = 5.5, fig.align = "center"}

dat_plot1 <- dat %>% 
  mutate(indic=ifelse(typology=="Ideological party", 1, 0)) %>% 
  group_by(party_id, family_name) %>% 
  mutate(nr_parties=sum(indic, na.rm=TRUE)) %>% 
  select(family_name, nr_parties, party_id) %>% 
  unique(.) %>% 
  ungroup(.) %>% 
  mutate(indic=ifelse(nr_parties>0, 1, 0)) %>% 
  group_by(family_name) %>% 
  mutate(total=n()) %>% 
  mutate(indic=sum(indic)) %>%
  select(-party_id, -nr_parties) %>% 
  unique(.) %>% 
  mutate(share=indic/total*100) %>% 
  mutate(no_party="Ideological party") %>% 
  rename(DV=no_party) %>%
  ungroup(.) %>% 
  arrange(share) %>% 
  mutate(ranking=row_number())

dat_plot2 <- dat %>% 
  mutate(indic=ifelse(typology=="Nonideological nonparty", 1, 0)) %>%  
  group_by(party_id, family_name) %>% 
  mutate(nr_parties=sum(indic, na.rm=TRUE)) %>% 
  select(family_name, nr_parties, party_id) %>% 
  unique(.) %>% 
  ungroup(.) %>% 
  mutate(indic=ifelse(nr_parties>0, 1, 0)) %>% 
  group_by(family_name) %>% 
  mutate(total=n()) %>% 
  mutate(indic=sum(indic)) %>%
  select(-party_id, -nr_parties) %>% 
  unique(.) %>% 
  mutate(share=indic/total*100) %>% 
  mutate(action_based="Nonideological nonparty") %>% 
  rename(DV=action_based)

dat_plot3 <- dat %>% 
  mutate(indic=ifelse(typology=="Nonideological movement", 1, 0)) %>% 
  group_by(party_id, family_name) %>% 
  mutate(nr_parties=sum(indic, na.rm=TRUE)) %>% 
  select(family_name, nr_parties, party_id) %>% 
  unique(.) %>% 
  ungroup(.) %>% 
  mutate(indic=ifelse(nr_parties>0, 1, 0)) %>% 
  group_by(family_name) %>% 
  mutate(total=n()) %>% 
  mutate(indic=sum(indic)) %>%
  select(-party_id, -nr_parties) %>% 
  unique(.) %>%  
  mutate(share=indic/total*100) %>% 
  mutate(catch_all_ref="Nonideological movement") %>% 
  rename(DV=catch_all_ref)

dat_plot <- bind_rows(dat_plot1, dat_plot2, dat_plot3) %>% 
  select(-ranking) %>% 
  ungroup(.) %>% 
  filter(!(family_name %in% c("to be coded", "Special issue", "no family"))) %>% 
  mutate(DV=case_when(DV=="Ideological party" ~ "Classical party\nname",
                      DV=="Nonideological nonparty" ~ "Nonideological\nnonparty name",
                      DV=="Nonideological movement" ~ "Nonideological\nmovement name")) %>%
  mutate(DV=factor(DV, levels=c("Classical party\nname", "Nonideological\nnonparty name", 
                                "Nonideological\nmovement name"))) %>% 
  # mutate(DV=fct_rev(DV)) %>% 
  mutate(family_name=factor(family_name, levels=c("Communist/Socialist", "Social democracy",
                                                  "Green/Ecologist", "Christian democracy", "Liberal", 
                                                  "Conservative", "Agrarian", "Right-wing"))) %>% 
  mutate(family_name=fct_rev(family_name))
  
rm(dat_plot1, dat_plot2, dat_plot3, totals)

# dat_plot$family_name <- factor(dat_plot$family_name, levels = unique(dat_plot$family_name[order(dat_plot$ranking, decreasing = FALSE)]))

rm(dat_plot1, dat_plot2, dat_plot3, totals)


ggplot(dat_plot, aes(y = family_name, x=share)) + #, fill=color_indic
  geom_col(color="black", show.legend = FALSE) + 
  facet_wrap(~DV, scales = "free_x", ncol=3) +
  scale_y_reordered() +
  xlab("Proportion of parties (pp. within party family)") +
  theme_linedraw() +
  # scale_fill_manual(name="", values=c("gray80", "gray40")) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE, reverse = TRUE)) +
  theme(legend.title=element_blank(), 
        legend.position="none",
        axis.title.y=element_blank())

ggsave(plot=last_plot(),
      filename = "Figure4_east.png",
      path="appendix/figures/", scale = 3,
      width = 6, height = 2.5, dpi=400, units="cm")

```

## Table 2: Distribution of brands in Eastern Europe


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}
dat <- dat %>% 
  mutate(dep_vars=case_when(typology=="Ideological party" ~ 1,
                            TRUE ~ 0))

groupped_share <- function(data, group_var) {

group_var <- enquo(group_var)

dat_plot <- dat %>% 
  mutate(past_pm = case_when(past_pm == "has been/is pm party" ~ 1,
                             past_pm == "no pm party" ~ 0),
         mainstream_family = case_when(family_name_short %in% c("chr", "con", "lib", "soc") ~ 1,
                                       TRUE ~ as.numeric(0)),
         opp_party = case_when(cabinet_party == 0 ~ 1,
                               cabinet_party == 1 ~ 0),
         econ_left = case_when(state_market>5 ~ 0,
                               state_market<=5 ~ 1),
         cult_progressive=case_when(liberty_authority>5 ~ 0,
                               liberty_authority<=5 ~ 1)) %>% 
  select(country, party_id, !!group_var, dep_vars) %>%
  group_by(country, !!group_var, dep_vars) %>% 
  mutate(by_var=n_distinct(party_id)) %>% 
  select(-party_id) %>% 
  unique(.) %>% 
  group_by(country, !!group_var) %>% 
  mutate(total=sum(by_var)) %>%
  ungroup(.) %>% 
  mutate(share=by_var/total) %>% 
  select(country, share, dep_vars, !!group_var, total) %>% 
  mutate(group_val=!!group_var) %>% 
  mutate(group_var=as_label(group_var)) %>% 
  unique(.) %>% 
  arrange(country, dep_vars) %>% 
  select(-!!group_var)

return(dat_plot)

}

dat_plot <- groupped_share(dat_plot, mainstream_family) 
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, past_pm))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, opp_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, new_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, econ_left))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, cult_progressive))

dat_plot <- dat_plot %>%
  arrange(country, group_var, dep_vars) %>%
  filter(!is.na(group_val)) %>%
  filter(dep_vars==1) %>% 
  select(-dep_vars)
  

full_list <- expand.grid(country=unique(dat_plot$country),
                         group_var=unique(dat_plot$group_var),
                         group_val=unique(dat_plot$group_val))

dat_plot <- left_join(full_list, dat_plot) %>% 
  mutate_at(vars(share, total), ~ifelse(is.na(.), 0, .)) %>% 
  group_by(group_var, group_val) %>% 
  mutate(share=mean(share)) %>% 
  mutate(total=sum(total)) %>% 
  select(-country) %>% 
  distinct(.) %>% 
  pivot_wider(id_cols = "group_var", names_from = "group_val", values_from = c("share", "total"))


for (i in seq(1, nrow(dat_plot), 1)) {

xsample <- sample(c(rep(1, round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0)), 
             rep(0, dat_plot$total_0[i]-round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0))))

ysample <- sample(c(rep(1, round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0)), 
             rep(0, dat_plot$total_1[i]-round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0))))

test <- t.test(xsample, ysample, alternative = "two.sided")

dat_plot$p_value[i] <- test$p.value

}

dat_plot <- dat_plot %>% 
  select(-contains("total")) %>% 
  mutate(p_value = case_when(p_value<0.05 ~ 1, 
                             TRUE ~ 0)) %>% 
  mutate(diff=share_0-share_1) 

ideological_party <- dat_plot  %>% 
  pivot_longer(cols=c(share_1, share_0), names_to = "dummy", values_to = "share") %>% 
  mutate(type = "Ideological party")

```


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}

dat <- dat %>% 
  mutate(dep_vars=case_when(typology=="Nonideological nonparty" ~ 1,
                            TRUE ~ 0))

dat_plot <- groupped_share(dat_plot, mainstream_family) 
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, past_pm))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, opp_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, new_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, econ_left))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, cult_progressive))

dat_plot <- dat_plot %>%
  arrange(country, group_var, dep_vars) %>%
  filter(!is.na(group_val)) %>%
  filter(dep_vars==1) %>% 
  select(-dep_vars)
  

full_list <- expand.grid(country=unique(dat_plot$country),
                         group_var=unique(dat_plot$group_var),
                         group_val=unique(dat_plot$group_val))

dat_plot <- left_join(full_list, dat_plot) %>% 
  mutate_at(vars(share, total), ~ifelse(is.na(.), 0, .)) %>% 
  group_by(group_var, group_val) %>% 
  mutate(share=mean(share)) %>% 
  mutate(total=sum(total)) %>% 
  select(-country) %>% 
  distinct(.) %>% 
  pivot_wider(id_cols = "group_var", names_from = "group_val", values_from = c("share", "total"))


for (i in seq(1, nrow(dat_plot), 1)) {

xsample <- sample(c(rep(1, round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0)), 
             rep(0, dat_plot$total_0[i]-round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0))))

ysample <- sample(c(rep(1, round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0)), 
             rep(0, dat_plot$total_1[i]-round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0))))

test <- t.test(xsample, ysample, alternative = "two.sided")

dat_plot$p_value[i] <- test$p.value

}

dat_plot <- dat_plot %>% 
  select(-contains("total")) %>% 
  mutate(p_value = case_when(p_value<0.05 ~ 1, 
                             TRUE ~ 0)) %>% 
  mutate(diff=share_0-share_1) 

nonideological_nonparty <- dat_plot %>% 
  pivot_longer(cols=c(share_1, share_0), names_to = "dummy", values_to = "share") %>% 
  mutate(type = "Nonideological nonparty")

```


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}

dat <- dat %>% 
  mutate(dep_vars=case_when(typology=="Nonideological movement" ~ 1,
                            TRUE ~ 0))

dat_plot <- groupped_share(dat_plot, mainstream_family) 
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, past_pm))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, opp_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, new_party))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, econ_left))
dat_plot <- bind_rows(dat_plot, groupped_share(dat_plot, cult_progressive))

dat_plot <- dat_plot %>%
  arrange(country, group_var, dep_vars) %>%
  filter(!is.na(group_val)) %>%
  filter(dep_vars==1) %>% 
  select(-dep_vars)
  

full_list <- expand.grid(country=unique(dat_plot$country),
                         group_var=unique(dat_plot$group_var),
                         group_val=unique(dat_plot$group_val))

dat_plot <- left_join(full_list, dat_plot) %>% 
  mutate_at(vars(share, total), ~ifelse(is.na(.), 0, .)) %>% 
  group_by(group_var, group_val) %>% 
  mutate(share=mean(share)) %>% 
  mutate(total=sum(total)) %>% 
  select(-country) %>% 
  distinct(.) %>% 
  pivot_wider(id_cols = "group_var", names_from = "group_val", values_from = c("share", "total"))


for (i in seq(1, nrow(dat_plot), 1)) {

xsample <- sample(c(rep(1, round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0)), 
             rep(0, dat_plot$total_0[i]-round(dat_plot$total_0[i]*dat_plot$share_0[i], digits = 0))))

ysample <- sample(c(rep(1, round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0)), 
             rep(0, dat_plot$total_1[i]-round(dat_plot$total_1[i]*dat_plot$share_1[i], digits = 0))))

test <- t.test(xsample, ysample, alternative = "two.sided")

dat_plot$p_value[i] <- test$p.value

}

dat_plot <- dat_plot %>% 
  select(-contains("total")) %>% 
  mutate(p_value = case_when(p_value<0.05 ~ 1, 
                             TRUE ~ 0)) %>% 
  mutate(diff=share_0-share_1) 

nonideological_movement <- dat_plot %>% 
  pivot_longer(cols=c(share_1, share_0), names_to = "dummy", values_to = "share") %>% 
  mutate(type = "Nonideological movement")

```


```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}

dat_plot <- bind_rows(ideological_party, nonideological_nonparty, nonideological_movement) %>% 
  filter(!(group_var %in% c("cult_progressive", "econ_left", "opp_party"))) %>% 
    mutate(group_var=case_when(group_var=="mainstream_family" & dummy=="share_1" ~ "Mainstream party family",
                               group_var=="mainstream_family" & dummy=="share_0" ~ "Challenger party family",
                        group_var=="past_pm" & dummy=="share_1" ~ "Previously PM party",
                        group_var=="past_pm" & dummy=="share_0" ~ "Previously no PM party",
                        group_var=="opp_party" & dummy=="share_1" ~ "Opposition party",
                        group_var=="opp_party" & dummy=="share_0" ~ "Government party",
                        group_var=="new_party" & dummy=="share_1" ~ "New party",
                        group_var=="new_party" & dummy=="share_0" ~ "Existing party")) %>%
  mutate(diff=ifelse(dummy=="share_0", NA, diff)) %>% 
  select(-dummy) %>% 
  pivot_wider(id_cols = c(group_var), values_from = c(p_value, share, diff), names_from = type) %>% 
  mutate(group_var=factor(group_var, levels = c("Mainstream party family",
                                                "Challenger party family",
                                                "Previously PM party", 
                                                "Previously no PM party",
                                                "Opposition party",
                                                "Government party",
                                                "New party",
                                                "Existing party"))) %>% 
  arrange(group_var)


ideological_party_pval <- dat_plot$`p_value_Ideological party`
nonideological_nonparty_pval <- dat_plot$`p_value_Nonideological nonparty`
nonideological_movement_pval <- dat_plot$`p_value_Nonideological movement`

dat_plot <- dat_plot %>% 
  select(!contains("p_value")) %>% 
  select("group_var", "share_Ideological party", "diff_Ideological party", "share_Nonideological nonparty", "diff_Nonideological nonparty", "share_Nonideological movement", "diff_Nonideological movement") %>% 
  mutate_at(vars(contains(c("share_", "diff_"))), ~round(.*100, digits = 1)) %>% 
  mutate_at(vars(contains(c("diff_"))), ~0-.) 

options(knitr.kable.NA = "")

mod_res <- dat_plot %>%
  kbl(caption = "Distribution of brands in Eastern Europe \\label{tab:ttest_table}",
      booktabs = T, format = "latex", col.names = NULL, linesep = "") %>% 
  # kable_styling(latex_options = c("hold_position")) %>% 
  kable_styling(latex_options = "HOLD_position") %>%   # Change will be here
  column_spec(3, bold = ideological_party_pval) %>%
  column_spec(5, bold = nonideological_nonparty_pval) %>%
  column_spec(7, bold = nonideological_movement_pval) %>%
  add_header_above(c(" " = 1, "Share" = 1, "Diff." = 1, "Share" = 1, "Diff." = 1, "Share" = 1, "Diff." = 1)) %>%
  add_header_above(c(" " = 1, "Classical \n party \n name" = 2, 
                        "Nonideological \n nonparty \n name" = 2, 
                        "Nonideological \n movement \n name" = 2)) %>% 
  footnote(general = "Note: The values are averaged across all countries.", general_title="")
  
writeLines(mod_res, "appendix/tables/Table1_east.tex")

```



```{r, echo = F, message = F, warning = F, fig.height = 5, fig.width = 10, fig.align = "center"}

```